Intentional release of native species undermines ecological stability

### 2022-12-24 rmd/manuscript.Rmd
edit: ms minor

**Model fitting.** We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016]. We assigned vague or weakly informative priors to parameters (**Table S**3). Four Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged. The total MCMC iterations ranged from `r min(df_mcmc$n_total_mcmc) %>% as.character()` to `r max(df_mcmc$n_total_mcmc) %>% as.character()`, in which MCMC samples were saved every `r unique(df_mcmc$n_thin)` steps for the calculation of posterior distributions after the initial `r max(df_mcmc$n_burn)` burn-in period. Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached $<1.1$ [@gelmanDataAnalysisUsing2007]. Data manipulation and analysis were performed in R version 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021]. Parameter estimates were summarized in **Tables S**4 -- **S**8.

>>>>

**Model fitting.** We fitted the models to the data using JAGS version 4.1.0 through *runjags* package version 2.2.0-2 in R [@denwoodRunjagsPackageProviding2016]. We assigned vague or weakly informative priors to parameters (**Table S**3). Four Markov chain Monte Carlo (MCMC) chains were run until parameter estimates converged. The total MCMC iterations ranged from `r min(df_mcmc$n_total_mcmc) %>% op(0)` to `r max(df_mcmc$n_total_mcmc) %>% op(0)`, in which MCMC samples were saved every `r unique(df_mcmc$n_thin)` steps for the calculation of posterior distributions after the initial `r max(df_mcmc$n_burn)` burn-in period. Convergence was assessed by examining whether the $\hat{R}$ indicator of each parameter approached $<1.1$ [@gelmanDataAnalysisUsing2007]. Data manipulation and analysis were performed in R version 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021]. Parameter estimates were summarized in **Tables S**4 -- **S**8.
